Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
add from and to date
removed a sentence about explaining the example. Move to discussion.

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history before June 13\textsuperscript{th}, 2012, which contains 6,605 changes and 72,484 comments.

@@

As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
Similarly, most comments in the red area are considered useless.
However, some comments were not determined (in white area).
From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
Some areas of these two models overlap, making results undeterminable.

>>>>

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history from May 25, 2011 to June 13, 2012, which contains 6,605 changes and 72,484 comments.

@@

As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
Similarly, most comments in the red area are considered useless.
However, some comments were not determined (in white area).
Some areas of these two models overlap, making results undeterminable.
